Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
updating markdown

---
title: "Implications of animal movement rate variation in spatial patterns of seed dispersal"
author: "Javiera Rudolph"
date: "8/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
```

@@

df %>% 
  ggplot(., aes(x = xloc, y = yloc)) +
  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  geom_bin2d() +
  # geom_hex() +
  # scale_fill_continuous(type = "viridis") +
  scale_fill_gradient(low = "grey", high = "black") +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(title = "Density of animal movement") -> p2
p2

@@

weib.boot
```

>>>>

---
title: "Implications of animal movement rate variation in spatial patterns of seed dispersal"
author: "Javiera Rudolph"
date: "8/12/2021"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=12, fig.height=6) 
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
```

@@

df %>% 
  ggplot(., aes(x = xloc, y = yloc)) +
  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  geom_bin2d() +
  # geom_hex() +
  # scale_fill_continuous(type = "viridis") +
  scale_fill_gradient(low = "grey", high = "black") +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(title = "Density of animal movement") -> p2
# p2

@@

# weib.boot
```
